---
name: Dr. Thejasvi 
surname: Beleyur
position: "Postdoctoral researcher"
address: ""
www: thejasvibr.github.io
email: "thejasvib@gmail.com"
github: thejasvibr
date: "`r format(Sys.time(), '%B %Y')`"
output: vitae::awesomecv
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(tinytex.verbose = TRUE)
library(vitae)
```

# Work Experience

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Description, ~ Where,
  "Research group leader (soon to be)", "March 2024 onwards" , "Group leader of the 'Active Sensing Collectives' research group " ,"Centre for the Advanced Study of Collective Behaviour (CASCB), Konstanz, Germany",
  "CASCB Postdoc Award", "Dec 1 2023 - Feb 28 2024", "Competitive award for promising postdocs looking to start their own groups.", "CASCB, Uni. Konstanz",
  "DFG Postdoctoral grant holder", "Aug 1 2022- Nov 30 2024", "DFG Walter Benjamin Awardee", "Dept. of Biology, Uni Konstanz, Germany",
  "Postdoctoral researcher", "April 1 2022-June 30 2022", "Extension contract for CASCB work", "CASCB, Uni. Konstanz",
  "Postdoctoral researcher", "March 15 2021-March 14 2022", "Developing analysis workflows to analyse the Ushichka dataset", "CASCB, Uni Konstanz",
  "Doctoral work on IMPRS contract", "June 1 2020- Nov 31 2020", "Modelling and multi-sensor tracking of free-flying bat groups", "Max-Planck Institute for Ornithology, Seewiesen, Germany",
  "Doctoral work on DAAD scholarship", "Sep 1 2015- Feb 28 2020", "Modelling and multi-sensor tracking of free-flying bat groups", "Max-Planck Institute for Ornithology, Seewiesen, Germany",
  "Research assistant and lab manager", "Aug 1 2014 - July 31 2015", "Social spider web construction and setting up undergraduate laboratory facilities", "Azim Premji University, Bengaluru, India",)  %>% detailed_entries(Description, Year,Position , Where)
```

# Breaks/part-time work in career

* 29/12/2022 - 28/2/2023 : full-time parental leave (Elternzeit)
* 29/12/2023 - 28/4/2024 : 60% full-time work on parental leave  (Elternzeit) 

# Education

```{r}
library(tibble)
tribble(
  ~ Degree, ~ Year, ~ Descr, ~ Where,
  "PhD", "2015-2021 (Defence: 10th June 2021)", "PhD thesis: Theoretical and empirical investigations of echolocation in bat groups", "University of Konstanz, Germany",
  "BS-MS dual degree in Biological Sciences", "2008-2013", "Masters thesis: Task differentiation during prey capture and retreat-mate recognition in the indian social spider, Stegodyphus sarasinorum (eresidae)", "IISER-Thiruvananthapuram, India",
) %>% 
  detailed_entries(Descr, Year, Degree, Where)
```


# Awards and grants

```{r}
library(tibble)
tribble(
  ~ Position, ~ Year, ~ Description, ~ Where,
  "Carl Zeiss Nexus grant", "2024" , "Research group grant promoting interdisciplinary science" ,"CASCB, Uni. Konstanz",
  "CASCB Postdoc Award", "2023", "Competitive award for promising postdocs looking to start their own groups.", "CASCB, Uni. Konstanz",
  "CASCB Postdoc grant", '2023', 'Postdoc grant for promising early-career researchers', 'CASCB, Uni. Konstanz',
  "CASCB Small grant", "2023", "Pilot grant to build a robotic bat platform", "CASCB, Uni. Konstanz",
  "Best Early Career Researcher talk", "2023", "IBAC 2023", "International Bioacoustics Society conference, Japan,2023",
  "Walter Benjamin Position", "2022.", " DFG Postdoctoral Grant", "Department of Biology, Uni. Konstanz",
  "Young Scholar Fund Award", "2022", "Bridge fellowship", "CASCB, Uni. Konstanz",
  "CASCB Medium Grant", "2021-2022", "Post doc grant", "CASCB, Uni Konstanz", 
  "IMPRS Bridge Award", "June 2020- Nov 2020", "Award to wrap up PhD", "IMPRS for Organismal Biology",
  "DAAD-GSSP scholarship", "2015-2020", "Scholarship awarded to pursue doctoral studies", "German Academic Exchange Service (DAAD)",
  "IMPRS best paper award", "2020", "Annual award given to best papers submitted in the graduate school.", "IMPRS for Organismal Biology",
"Google Cloud Platfrom Research Credits", "2019", "A 1000$ grant that provides access to cloud computing resources to execute simulations for Beleyur & Goerlitz 2019", "Google Cloud",
  "IMPRS travel grant", "2017", "Travel grant awarded to attend the SNAK 2018 acoustics course in Odense, Denmark", "IMPRS for Organismal Biology") %>% 
  detailed_entries(Description, Year,Position , Where)
```


# Publications

```{r}
library(dplyr)
#knitr::write_bib(c("vitae", "tibble"), "packages.bib")
bibliography_entries("publications.bib") 
```
\newpage 

# Mentoring

```{r mentoring}
library(flextable)
library(kableExtra)
mentorship <- read.csv('mentorship.csv')
colnames(mentorship) <- c('Name', 'Year', 'Title', 'Degree', 'Affiliation', 'Co-supervisors')
mentorship$Year <- as.character(mentorship$Year)
kable(mentorship) %>% column_spec(1,  latex_valign='m') %>% column_spec(2,  latex_valign='m') %>% column_spec(3, width='5cm', latex_valign='m') %>% column_spec(4, width='2cm', latex_valign='m') %>% column_spec(5, width='2cm', latex_valign='m') %>% column_spec(6, width='3cm',latex_valign='m')
#ft <- flextable(mentorship)
#ft


# knitr::kable(mentorship, format='latex')

# Person, degree + Affiliation , Year, Title, Supervisors
#mentorship_ <- c('Alberto Doimo', 'Masters thesis, Technical University of Milan', '2024', 'RO-BAT: a bat-inspired approach on mobile robot navigation using Direction of Arrival estimation', 'Co-sup. with #Dr. Andreagiovanni Reina, Prof. Heiko Hammann - Uni. Konstanz' )
#mentorship_1 <- c('Clare Guerin', 'Erasmus Mundus Project, LMU Munich', '2016', 'Quantifying potential #sensory interference in bat aggregations', 'Co-sup. with Dr. Holger Goerlitz - MPI Ornithology, Seewiesen')

#mentorship_df <- data.frame(c(mentorship_, mentorship_1))
#formattable(mentorship_df)


```


# Teaching 

## Lectures

* 2024 'Animal Behaviour' undergraduate course (Uni. Konstanz) lecture on *Sensory ecology, animal behaviour  and collectives*

* 2023 lecturer at the Konstanz School of Collective Behaviour, Uni. Konstanz, *Acoustic tracking from easy to crazy*

## In-house talks and workshops on software and coding practices

* *Version Control for Organismal Biologists*: introductory workshop on why one should use version control and how to do it with Git (3 workshops so far)
* *Python for Organismal Biologists*: introductory workshop on using Python for scientific computing with example code and Jupyter notebooks that participants run during the workshop (2 workshops so far)



# Scientific software packages
I strive to make the code I write for various projects as modular and re-usable as possible while adopting software development best practices. A selection of packages that I've written, along with a short description. 

* ```beamshapes```: computational implementations of various sound-radiation models. The models can be used to perform predictions for planned experiments, or parameter inference.  [*Paper hyperlink*](https://joss.theoj.org/papers/10.21105/joss.03740). [*Online docs hyperlink*](https://beamshapes.readthedocs.io/en/latest/)

* ```itsfm```: segments sounds based on frequency modulation. Various inbuilt and custom measurements can also be performed on the segmented audio. [*Preprint hyperlink*](https://www.biorxiv.org/content/10.1101/2021.01.09.426033v1). [*Online docs hyperlink*](https://itsfm.rtfd.io)

* ```batracker``` (*under development*): a bat-centric acoustic tracking package developed to handle simple (single-few bats, clean recordings) to complex (multiple bats, overlapping calls, reverberance) datasets using the latest in signal analysis and tracking algorithms. To my knowledge, this is the first bat-centric open-source package in development. [*Online docs hyperlink*](https://batracker.rtfd.io)

\newpage 
# Technical skills 

* Acoustic and video tracking of animals 
* Design, execution and analysis of bioacoustics and animal behaviour experiments
* Experience handling animals (ants, spiders, bats) and managing field work
* Signal and image analysis, digital data acquisition methods
* Writing readable and reproducible scientific code
* Coding in order of language proficiency: Python, R, MATLAB
* Writing and maintaining scientific software packages



## Other Competencies

* Scientific manuscript and grant writing
* Track record of working in interdisciplinary environments 
  
## Languages spoken (self-assessed CEFR levels)
The CEFR ([link](https://en.wikipedia.org/wiki/Common_European_Framework_of_Reference_for_Languages)) has three divisions (A: basic user, B: independent user, C: proficient user). Each divisons has two levels (1,2).

* English: C2 (proficiency)
* German: B1 (upper intermediate)
* Kannada: B1
* Hindi: B1
* Bahasa Indonesia: A2 (elementary)


# Public outreach

My German is good enough to allow semi-technical conversations that convey my enthusiasm for bats, echolocation and the techniques we use to study them. I use the various opportunities to interact with the public:

* September 2018, 'Fledermausführung': I co-led a 'bat walk' session for a group of school children while talking about the biology, behaviour and techniques related to bats. 
* July 2017, BIOTOPIA Stadtteilfest: I was in charge of explaining various exhibits highlighting animal and plant forms as part of a one-day even to increase public awareness of the then newly opened BIOTOPIA museum.
* June 2017, Tag der Oeffenen Tür: Open day at the Max-Planck Institute for Ornithology, Seewiesen. I was part of an exhibit showcasing various aspects of bat biology and echolocation research done in my former lab. 
* January 2017, BIOTOPIA inaugration event: I had an exhibit showing a live feed of a single thermal camera as people walked by, explaining how it works, and how we use them in our research studying bats in the dark.
